Towards a Mechanized Proof of Noninterference

### 2013-12-19 paper/paper.tex
earlyoften

Furthermore, primarily due to a matter of taste, we decided to replace the
\textsf{case} construct from \origLang for an \textsf{if} construct, which
evaluates the first expression if the test evaluates to 1 and evaluates to the
second expression otherwise.

\langName, like \origLang, includes angle bracketed expressions, which represent
values or expressions which could differ between two runs of the program.  As we
will see when discussing the type system, this corresponds to values and
expressions that have high security labels on their types.

Through these changes, our language has the syntax shown in
Figure~\ref{fig:syntax}.  As shown, final states, answers, in the language are
now simple values because there are no exceptions.

@@

    \infer[G-Int]
    {
    l \leq l'
    }
    {
    l \guards (* \to *)^{l'}
    }
  \end{mathpar}
  \caption{Rules for labels guarding types in \langName.}
  \label{fig:guard_rules}
\end{figure}

>>>>

We also decided to replace the
\textsf{case} construct from \origLang with an \textsf{if} construct, which
evaluates the first expression if the test evaluates to 1 and evaluates to the
second expression otherwise.

\langName, like \origLang, includes angle bracketed expressions which represent
values or expressions which could differ between two runs of the program.  As we
will see when discussing the type system, this corresponds to values and
expressions that have high security labels on their types.

Through these changes, our language has the syntax shown in
Figure~\ref{fig:syntax}.  As shown, final states (answers) in the language are
now simple values because there are no exceptions.

@@

    \infer[G-Abs]
    {
    l \leq l'
    }
    {
    l \guards (* \to *)^{l'}
    }
  \end{mathpar}
  \caption{Rules for labels guarding types in \langName.}
  \label{fig:guard_rules}
\end{figure}
